Twang only analysis summary

### 2025-06-23 twang-analysis.Rmd
fix up save

# Save the plots
ggsave("forest_plot_subgroups_only.png", plot_subgroups, 
       width = 10, height = 8, dpi = 300, bg = "white")
ggsave("forest_plot_with_overall.png", plot_with_overall, 
       width = 10, height = 8.5, dpi = 300, bg = "white")

# Also save extracted data for reference
write.csv(forest_data, "forest_plot_data.csv", row.names = FALSE)

>>>>

# Create images directory if it doesn't exist
if (!dir.exists("images")) {
  dir.create("images")
}

# Save the plots
ggsave("images/forest_plot_subgroups_only.png", plot_subgroups, 
       width = 10, height = 8, dpi = 300, bg = "white")
ggsave("images/forest_plot_with_overall.png", plot_with_overall, 
       width = 10, height = 8.5, dpi = 300, bg = "white")

# Also save extracted data for reference
write.csv(forest_data, "images/forest_plot_data.csv", row.names = FALSE)
